Circular Distributional Trees and Forests with an Application to Wind Direction Forecasting

### 2019-11-19 pkg/circtree/inst/wind_paper/draft/draft.Rnw
Minor modifications in plot nad updated example tree
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2881 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: da29af6c8add406f14141edeb255443a54d4e246
Update title
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2883 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 06c6edcaf85dc58a1875050563ba326df1176af9

\title{Circular Trees and Forests with an Application to 
    Probabilistic Wind Direction Forecasting}
\Shorttitle{Circular Trees and Forests}

@@

\section{Case study: Probabilistic wind direction forecasting}
\label{sec:wind}
Accurate forecasts of wind directions are of great importance for risk
management in various fields such as agriculture, energy production or air safety control. 
For example in order to direct airplanes to a safe landing, precise knowledge of wind 
direction at the respective airport for the next hour(s) is highly desirable and adequate 
prediction methods are required. In this section, a comprehensive case study on probabilistic
wind direction forecasting is provided for two airports in Austria with fundamentally
different site characteristics: Innsbruck with a rather unusual location for an
airport, located at the bottom of a deep alpine valley, and Vienna located
within flat terrain in the East of Austria. In addition to the newly
introduced circular distributional trees and forests, the case study employs various
alternative approaches to forecast wind direction. The study is based on
$1$\,h and $3$\,h forecasts employing lagged observations in the vicinity of
the airports.

>>>>

\title{Circular Distributional Trees and Forests with an Application to 
    Wind Direction Forecasting}
\Shorttitle{Circular Trees and Forests}

@@

\section{Case study: Probabilistic wind direction forecasting}
\label{sec:wind}
Accurate forecasts of wind directions are of great importance for risk
management in various fields such as agriculture, energy production or air safety control. 
For example in order to direct airplanes to a safe landing, precise knowledge of wind 
direction at the respective airport for the next hour(s) is highly desirable and adequate 
prediction methods are required. In this section, a comprehensive case study on probabilistic
wind direction forecasting is provided for two airports in Austria with fundamentally
different site characteristics: Innsbruck with a rather unusual location for an
airport, located at the bottom of a deep alpine valley, and Vienna located
within flat terrain in the East of Austria. In addition to the newly
introduced circular distributional trees and forests, the case study employs various
alternative approaches to forecast wind direction. The study is based on
$1$\,h and $3$\,h forecasts employing lagged observations in the vicinity of
the airports as predictor variables.
